MCMC convergence diagnostics

### 2023-01-15 src/naomi-simple_mcmc/mcmc-convergence.Rmd
20,000 x 4 back from DIDEHPC

This MCMC took `r as.numeric(out$time)` minutes to run

@@

```{r}
nb <- area_merged %>%
  filter(area_level == max(area_level)) %>%
  bsae::sf_to_nb()

>>>>

This MCMC took `r out$time` to run

@@

```{r}
area_merged <- sf::read_sf(system.file("extdata/demo_areas.geojson", package = "naomi"))

nb <- area_merged %>%
  filter(area_level == max(area_level)) %>%
  bsae::sf_to_nb()
